LAs_clusters k = 9

### 2021-03-11 paper/v2_taylor_francis/response_reviewers.md

---
output:
  pdf_document: default
bibliography: bibliography.bib
---
Dear Prof. Bian,

@@

Kind Regards,

[removed for anonymity]

## Reviewer: 1

> The paper reports research of detecting clusters of network access speed, especially under the pandemic for resilience. Such a topic is of great importance as we are all in the pandemic and we rely on the network cyberinfrastructure for work as stated, and also for online education for all levels of students. Therefore, it worth supports with a few major revisions needed:

Thank you for your very supportive comments.

@@

> 1. The VGI approach of obtaining network speed maybe bias given that this probably is the digital guru group that will respond, maybe a discussion on this and picture the steps of selecting/soliciting and how representative this is.

We have added the following sentence to the first paragraph in section 3.2, explaining why we believe any bias balances out: 
"Indeed, those who seek to test their broadband are most likely to do so because 
they are experiencing slower speeds than expected, although any skew towards slower
speeds is balanced by the likelihood that those who test their broadband are also 
more 'tech-savvy' and / or have purchased higher speed packages that are not 
delivering the promised level of service."

As we explain, our intentions were to analyse a dataset of experienced internet speeds.
Those who use the speedcheck service are not solicited in any way, and no personally 
identifying data is included other than the geolocation of the test.

@@

> 2. The results for network speed for the different regions are not very different with 1-2 out of 10Mbps difference and probably can not reflect the social disparities. Not sure if this is the facts in U.K. If so, then it's not a problem?

Firstly, mean speeds are not likely to be that different between regions of the UK 
(e.g. North or South England). The greater differences are between urban, built-up 
areas, and more rural areas within regions, although there are some local initiatives 
to address this in some areas. However, we assume that your comment refers to Table 1 
and the differences in mean network speed between clusters? Whilst these differences 
are not large, the range for upload speeds is smaller than for download speeds, 
and a difference of 1-2Mbps slower may well be noticeable at the wrong moment. 
Importantly, we only consider the test which took place during working hours, so 
when speed drops during, let's say, a work Zoom call or when uploading large files,
it will be noticeable. This is why we created the clusters by how the time series 
of speeds changes by day of the week and hour of the day, rather than focusing our 
analysis on mean speeds.

@@

> 3. The relevance to pandemic is not very straightforward. This may be improved by adding some studies, e.g., how the clusters impact the effectiveness of work from home through survey. Or relates to the employment rate.

Regrettably, we did not have the opportunity to run a survey. As we say in the introduction, 
prior to the pandemic, the demand for telecommuting would not have put a strain 
on internet connection speeds. We have clarified this with the addition of the following sentence:
"High levels of demand are one of the main causes of reduced reliability and slower connection speeds, as network bandwidth becomes congested".

**Also consider whether we add % furlough to regression? https://www.gov.uk/government/statistics/coronavirus-job-retention-scheme-statistics-june-2020**

@@

> 4. The time series may be enhanced by putting a time range according to different events of the pandemic or other factors that relates to the pandemic.

We chose the time range to reflect the period of first lockdown in the UK, as we say in the first paragraph of 3.2: 
"We are particularly interested in upload speeds and the frequency of speed tests
over the period from March to May $2020$, as government statements indicate this 
encompasses the period when UK workers were first told to work from home if at all 
possible [@GovUK2020]".

We have also added the following text:
"Schools and various retail, leisure and hospitality businesses were closed from late 
March, and restrictions were gradually eased from late May".

@@

> 5. Would suggest a review of the spatiotemporal challenges of the covid-19.

??

> 6. A review of cyberinfrastructure and how network varies in different region would be useful.

In section 2.2 of the literature review, we have added additional detail specific to the UK:

"This finding broadly applies in the UK, where studies that also analysed broadband 
speed checks concluded that average speeds are lower in rural areas, something that
has not been improved by policy measures to increase competition [@riddlesden2014broadband; @nardotto2015unbundling].
@riddlesden2014broadband found that levels of deprivation did not correlate with 
first level digital divides".

and

"Dense urban areas were shown to suffer more from slow down during peak hours, 
although these services were more likely to be improved by increased competition 
between providers, such as between new entrants and Virgin Media cable connections
[@riddlesden2014broadband; @nardotto2015unbundling]. The latter were historically 
available to only $45$% of premises in the UK [@ofcom2016], where the more
lucrative and competitive market originally attracted the cable TV provider".

The latter bit about Virgin Media is moved from the results section, in response to reviewer 2, q7.

@@

> 7. The first part introduction can be shorted to reflect the importance of network bandwidth to resilience of pandemic impacted life.

As mentioned in response to comment 3, we have added a sentence of clarification 
to highlight the link between speed and bandwidth. We have also restructured the 
introduction, so this becomes the second paragraph, the 3rd paragraph is slightly 
shorter, and we introduce our case study approach in the 4th paragraph. We also 
moved the paragraph describing the three levels of digital divides to the literature review.

@@

> 5.  There are three levels of digital divide. According to the last paragraph in Section 2, only the intersection of level-1 and level-3 was included in this research. I am wondering how level-2 may fit in the general research framework. Could education and demographic variables be used to represent level-2 digital divide?

> 6. A few suggestions on the figures. Fig 1 and 2 have crowded tick labels for x-axis month and weekday. Fig 3 and 4 may be placed side by side with the same y-axis for easy comparison. Actually, I feel “Figure 3 shows that the high standard deviation” may be inaccurate as Fig 4 appears to exhibit higher variability. Fig 5 maps may include the locations of metropolitan or major cities to help interpretation. The warmer-cooler color scheme may match the population size instead of the ordinal cluster numbers. The current color scheme does not help interpretation at all.

> 7. A few minor things. In Sec 2.2, the statement “These returns have been even greater …” appears to be controversial. LAD acronym appears before it was defined. Virgin Media as a major broadband provider should be briefly introduced in the manuscript.

We have toned down the statement on returns to say:
"In some aspects, these returns may have increased during the Covid-19 crisis..."

Apologies on LAD acronym, now corrected.

We also moved and integrated introduction of Virgin Media to the literature review s2.2. See also response to reviewer 1, q6.

### 2021-03-11 src/LAs_Clusters_k9.Rmd
regressions for k=9

```{r settings, include = FALSE}
library(ggplot2)
library(tidyverse)
library(rprojroot)
library(lubridate)
library(knitr)
library(rprojroot)
library(nnet)
library(stargazer)
library(openair)
library(rgdal)
library(corrplot)
library(DescTools)
library(geosphere)
library(rgeos)
library(raster)
library(httr)
library(readxl)

@@

@@

```{r}
data.old.path <- paste0(path, "/data/temp/data_for_aux.csv")
data <- read_csv(data.old.path) %>% 
  dplyr::select(-c(1,4:19)) %>% 
  left_join(x = lad, y = . )

@@

data.cor <- data %>%
  dplyr::select(LAD.tests.am20,
                pop, pop16_64,
                managers, tech,
                skilled, earnings,
                total.busi)

data.cor <- data %>%
  dplyr::select(pop16_64, 
                pop.dens,
                job.dens2018, 
                distMet,
                distLondon,
                south,
                managers, 
                tech,
                skilled,
                prof,
                admin, 
                caring,
                plant,
                earnings,
                total.busi,
                LAD.tests.am20,
                pop,
                virgin) %>%
  mutate('LAD.tests.am20/pop' = LAD.tests.am20/pop) %>%
  mutate('total.busi/pop' = total.busi/pop) %>%
  dplyr::select(-LAD.tests.am20,-pop, -total.busi)

@@

aux.up <- multinom(cluster.up ~ 
                     #pop16_64 + # non sign, while pop is
                     pop +
                     #pop.dens + 
                     job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                     distMet + distLondon + south +
                     managers + tech + skilled + prof + admin + caring + plant +
                     earnings + I(total.busi/pop) + nvq4 +
                     I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                     virgin
                   , data = data, 
                   trace = F) # to avoid messages

@@

stargazer(aux.up, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
            "pop, 2018",
            #"pop. densuty, 2018",
            "job density, 2018",
            "distance to nearest met. area",
            "distance to London",
            "South of the UK",
            "% of managerial jobs, 2020",
            "% of tech jobs, 2020",
            "% of skilled trade jobs, 2020",
            "% of professional jobs, 2020",
            "% of administrative jobs, 2020",
            "% of leisure jobs, 2020",
            "% of machine operation jobs, 2020",
            "earnings, 2019",
            "n. business est. per hab., 2019",
            "% of NVQ4+",
            "n. of AM broadband tests per hab., 2020",
            "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3)
                             , round(r2.up[1],3), round(r2.up[1],3)),
                           (c("N",
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs
                              , n.obs, n.obs))))

>>>>

```{r settings, include = FALSE}
library(ggplot2)
library(tidyverse)
library(rprojroot)
library(lubridate)
library(knitr)
library(rprojroot)
library(nnet)
library(stargazer)
library(openair)
library(rgdal)
library(corrplot)
library(DescTools)
library(geosphere)
library(rgeos)
library(raster)
library(httr)
library(readxl)
library(httr)

@@

## furlough

```{r}
url <- "https://assets.publishing.service.gov.uk/government/uploads/system/uploads/attachment_data/file/891607/Coronavirus_Job_Retention_Scheme_Statistics_Tables_June_2020.xlsx"
GET(url, write_disk(tf <- tempfile(fileext = ".xlsx")))
f <- readxl::read_excel(tf, 6L, range = "B7:D486", col_names = F) %>% 
  rename(lad19cd = 1,
         lad19nm = 2,
         furlough = 3) %>% 
  filter(!is.na(furlough) & !is.na(lad19cd)) %>% 
  dplyr::select(-lad19nm)
```

@@

```{r}
data.old.path <- paste0(path, "/data/temp/data_for_aux.csv")
data <- read_csv(data.old.path) %>% 
  dplyr::select(-c(1,4:19)) %>% 
  left_join(x = lad, y = . ) %>% 
  left_join(x = ., y = f )

@@

# data.cor <- data %>%
#   dplyr::select(LAD.tests.am20,
#                 pop, pop16_64,
#                 managers, tech,
#                 skilled, earnings,
#                 total.busi)

data.cor <- data %>%
  dplyr::select(#pop16_64,
                pop,
                #pop.dens,
                job.dens2018, 
                distMet,
                distLondon,
                south,
                managers, 
                tech,
                skilled,
                prof,
                admin, 
                caring,
                plant,
                earnings,
                total.busi,
                nvq4,
                furlough,
                LAD.tests.am20,
                virgin) %>%
  mutate('LAD.tests.am20/pop' = LAD.tests.am20/pop) %>%
  mutate('total.busi/pop' = total.busi/pop) %>%
  mutate('furlough/pop' = furlough/pop) %>% 
  dplyr::select(-LAD.tests.am20,-pop, -total.busi, -furlough)

@@

aux.up <- multinom(cluster.up ~ 
                     #pop16_64 + # non sign, while pop is
                     pop +
                     #pop.dens + 
                     job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                     distMet + distLondon + south +
                     managers + tech + skilled + prof + admin + caring + plant +
                     earnings + I(total.busi/pop) + nvq4 + I(furlough/pop) +
                     I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                     virgin
                   , data = data, 
                   trace = F) # to avoid messages

@@

stargazer(aux.up, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
            "pop, 2018",
            #"pop. density, 2018",
            "job density, 2018",
            "distance to nearest met. area",
            "distance to London",
            "South of the UK",
            "% of managerial jobs, 2020",
            "% of tech jobs, 2020",
            "% of skilled trade jobs, 2020",
            "% of professional jobs, 2020",
            "% of administrative jobs, 2020",
            "% of leisure jobs, 2020",
            "% of machine operation jobs, 2020",
            "earnings, 2019",
            "n. business est. per hab., 2019",
            "% of NVQ4+",
            "% furloughed pop., 2020",
            "n. of AM broadband tests per hab., 2020",
            "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3)
                             , round(r2.up[1],3), round(r2.up[1],3)),
                           (c("N",
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs
                              , n.obs, n.obs))))

## Auxiliary regression, dep. var.: upload clusters, NO NVQ4

```{r upload regression no NVQ4, results= 'asis', message=F, error=F, warning=F}
aux.up <- multinom(cluster.up ~ 
                     #pop16_64 + # non sign, while pop is
                     pop +
                     #pop.dens + 
                     job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                     distMet + distLondon + south +
                     managers + tech + skilled + prof + admin + caring + plant +
                     earnings + I(total.busi/pop) + I(furlough/pop) +
                     I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                     virgin
                   , data = data, 
                   trace = F) # to avoid messages

stargazer(aux.up, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
            "pop, 2018",
            #"pop. density, 2018",
            "job density, 2018",
            "distance to nearest met. area",
            "distance to London",
            "South of the UK",
            "% of managerial jobs, 2020",
            "% of tech jobs, 2020",
            "% of skilled trade jobs, 2020",
            "% of professional jobs, 2020",
            "% of administrative jobs, 2020",
            "% of leisure jobs, 2020",
            "% of machine operation jobs, 2020",
            "earnings, 2019",
            "n. business est. per hab., 2019",
            "% furloughed pop., 2020",
            "n. of AM broadband tests per hab., 2020",
            "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3)
                             , round(r2.up[1],3), round(r2.up[1],3)),
                           (c("N",
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs
                              , n.obs, n.obs))))
